Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-23 doc/asplos13/abstract.tex
pass on abstract

Grappa is a latency tolerant runtime system for commodity multinode multicore
platforms that addresses the challenges posed in scaling irregular parallel
applications to large datasets. These applications are of growing importance
as interactive analysis of large unstructured data sets emerges as a
commercial and government priority. Grappa serves both as a C++ user library
and as a foundation upon which higher level languages can be developed or
adapted to support development of irregular parallel applications. Grappa
tolerates the delays to distant memory by multiplexing hundreds to thousands
of lightweight tasks to each processor core; balances load via fine-grained
workstealing; and provides efficient synchronization and consistency across
its single shared address space. We present a detailed description
of the Grappa system, programming examples using the library interface, and
compare performance for several irregular benchmarks to the Cray XMT, a custom
system used to target the real time graph analytics market.

>>>>

Grappa is a latency tolerant runtime system for commodity clusters of
multicore computers, its goal is to provide scalable performance for irregular
parallel applications. These applications are of growing importance as
interactive analysis of large data sets emerges as a commercial and government
priority, typically in the form of graph processing. Grappa serves both as a
C++ user library and as a foundation upon which higher level languages can be
developed or adapted to support development of irregular parallel
applications. Grappa tolerates the delays to distant memory by multiplexing
thousands of lightweight tasks to each processor core; balances load via
fine-grained distributed work-stealing; takes full advantage of network
characteristics by aggregating smaller requests into large ones; and provides
efficient synchronization and remote operations across its single shared
address space. We present a detailed description of the Grappa system,
programming examples using the library interface, and compare performance for
several irregular benchmarks to the Cray XMT, a custom system used to target
the real time graph analytics market.
